\documentclass[line, margin, 10pt]{res}
\setlength{\parskip}{9pt}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage[T1]{fontenc}

\begin{document}

\renewcommand{\namefont}{ \LARGE \bf }
% \renewcommand{\titlefont}{ \bf }

\name{Ryan Watkins}

\begin{resume}

\section{\textsc{Contact Information}}
Surrey,  \hfill{ryanwatkins54@gmail.com}\\
London \hfill{(+44) 7565 646 983 }\\
United Kingdom 

\section{\textsc{Experience}}

% Not using the position element here, as I don't like the formatting options.

{\bf Feistybird}, London, United Kingdom \\
\textit{Founding Engineer and CTO} \hfill {\bf September 2014 - Now}\\
Founded and developed 'Feistybird', a service that moderates and displays social feeds from hashtags, adds event agendas and customizes the final display layout.
Technologies used include SQL, JS, PHP, React, AWS, Unix, CSS and HTML

{\bf Allianz Global Investors GmbH}, Munich, Germany\\
{\it Frontend Developer (Internship)} {\bf \hfill July 2015 - September 2015}\\
Improved UX/UI for 'TimeScape Explorer' (Investing UI). Integrated various open source libraries into the existing ASP.NET framework such as 'Handsontable' and 'MetricGraphics'.
 Coordination with project integrating new database schema. Performance optimization on large datasets from SQL database. Technologies used were Git, jQuery, ASP.NET and JS.

{\bf Sixt GmbH \& Co. Autovermietung KG}, Munich, Germany\\
{\it Full Stack / Scala Developer} {\bf \hfill August 2016 - January 2017}\\
Golang API/middleware, ReactJS/Redux. Scala.

\section{\textsc{Education}}
{\bf Bachelor of Science}, University of Reading {\bf \hfill September 2013 - July 2016}\\
Grade: First Class \\
\\
\begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}
\bf{Modules(Y1):}  & Computer Architecture,
  Programming, 
  Software Engineering,
  Maths for Computer Science,
  Fundamentals of Computing,
  Computer Applications,
\end{tabular}

\begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}  
\bf{Modules(Y2):}  & Compilers,
  Operating Systems,
  Neural Networks,
  Machine Intelligence,
  Java,
  Computer Architecture,
  Advanced Databases,
  Databases,
  Essential Algorithms,
  Systems Design and Project Management
\end{tabular}

\begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}  
\bf{Modules(Y3):}  & Social, Legal and Ethical Aspects of Science and Engineering,
  Individual Project,
  Data Mining,
  Concurrent Systems,  
  Evolutionary Computation,
  Virtual Reality,
  Computer Networking
\end{tabular}

\section{\textsc{Skills}}
   \begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}
     \bf{In Production:} & JS, React, Node.js, PostgresSQL, Bash, Linux, AWS \\
    \\
    \bf{In General:} & C\#, C++, Java, C  \\
    \\
    \bf{Preferred Stack:} & Node.js, React, Git, ReasonML, Bash, Clojure/Haskell \\
 \end{tabular}

\section{\textsc{Projects}}

{\bf SQASM: Simple Quantum Assembly} {\bf \hfill 2016}\\
BSc. Thesis in Computer Science. A full PL that simulates quantum computation.\\ Technologies used: Python, C, YACC and LEX.\\ 
GitHub Repository: \url{http://github.com/watkinsr/SQASM}

{\bf 2D SDL RPG Engine (C++)} {\bf \hfill 2013}\\
Framework to allow developers to make their own 2D RPG's. \textit{100\% grade awarded} in first semester. Over 3000 lines of code.  \\
GitHub Repository: \url{http://github.com/watkinsr/SDL-RPG}

\\\\\\\\\\
{\bf Quantum Computing for Computer Scientists Drills {\bf \hfill 2015}} \\
Exercises completed from the book: Quantum Computing for Computer Scientists. Programmed in Python to illustrate quantum computing concepts.\\
GitHub Repository: \url{https://github.com/watkinsr/QuantumComputingDrills}

{\bf Breakout - Android Game (Java) {\bf \hfill 2015}} \\
Android breakout game. Contains a few advanced features (you can control two paddles and there are multiple balls)\\
GitHub Repository: \url{https://github.com/watkinsr/breakout}

\section{\textsc{Community Involvement}}

{\bf Mentor for Android Game Development MOOC}, FutureLearn Ltd {\bf \hfill 2014-2016}\\
Answering various Java and Android related questions from participants

\section{\textsc{Honors}}

{\bf Software Engineering Winner}, University of Reading {\bf \hfill 2014}\\
{\bf Best Team Participation (The EDGE Project)}, Carshalton College {\bf \hfill 2013}

\section{\textsc{Languages}}
\begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}

\textbf{English} & Native\\ 
\textbf{German} & Professional\\ \textbf{Chinese} & Basic

\end{tabular}

\end{resume}
\end{document}
