\documentclass[line, margin, 10pt]{res}
\setlength{\parskip}{9pt}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage[T1]{fontenc}

\begin{document}

\renewcommand{\namefont}{ \LARGE \bf }

\name{Ryan Watkins}

\begin{resume}

\section{\textsc{Contact Information}}
London,  \hfill {ryanwatkins54@gmail.com}\\
United Kingdom \hfill {(+44) 7565 646 983 }\\

\section{\textsc{Experience}}

{\bf Red Ant}, London, United Kingdom {\hfill September 2017 -  Now}\\
{\it Full Stack Developer} \\
Node.JS, React/Redux, React-Native, Meteor, TDD.

{\bf Sixt GmbH \& Co. Autovermietung KG}, Munich, Germany {\hfill August 2016 - January 2017}\\
{\it Full Stack / Scala Developer} \\
Golang API/middleware, ReactJS/Redux. Scala.

{\bf Feistybird}, London, United Kingdom \\
\textit{Founding Engineer and CTO} \hfill {September 2014 - July 2015}\\
Founded and developed 'Feistybird', a twitterwall as a service.

{\bf Allianz Global Investors GmbH}, Munich, Germany\\
{\it Frontend Developer (Internship)} {\hfill July 2015 - September 2015}\\
UX/UI for 'TimeScape Explorer' (Investing UI).

\section{\textsc{Education}}
{\bf First Class Hons. BSc. Computer Science}  {\hfill September 2013 - July 2016}\\
University of Reading

\begin{tabular}[t]{@{} p{1.2in} p{4.5in} @{}}
\bf{First Year}  & Computer Architecture,
  Programming, 
  Software Engineering,
  Maths for Computer Science,
  Fundamentals of Computing,
  Computer Applications,
\end{tabular}

\begin{tabular}[t]{@{} p{1.2in} p{4.5in} @{}}  
\bf{Second Year}  & Compilers,
  Operating Systems,
  Neural Networks,
  Machine Intelligence,
  Java,
  Computer Architecture,
  Advanced Databases,
  Databases,
  Essential Algorithms,
  Systems Design and Project Management
\end{tabular}

\begin{tabular}[t]{@{} p{1.2in} p{4.5in} @{}}  
\bf{Third Year}  & Social, Legal and Ethical Aspects of Science and Engineering,
  Individual Project,
  Data Mining,
  Concurrent Systems,  
  Evolutionary Computation,
  Virtual Reality,
  Computer Networking
\end{tabular}

\section{\textsc{Skills}}
   \begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}
     \bf{In Production:} & JS, React, Node.js, PostgresSQL, Bash, Linux, AWS, Golang \\
    \\
    \bf{In General:} & Node.js, Bash, Lisp  \\
    \\
    \bf{Preferred Stack:} & Clojure/Haskell, Common Lisp, Bash, Scala, Ocaml \\
 \end{tabular}

\section{\textsc{Github}}
{\bf \url{https://github.com/watkinsr}}\\

\section{\textsc{Projects}}

{\bf Next-Browser} {\bf \hfill 2018}\\
Open source involvement in Next Browser, a web browser for professional productive individuals.\\
Source: \url{https://github.com/next-browser/next}\\

{\bf Simple Quantum Assembly (Thesis)} {\bf \hfill 2016}\\
A full PL that simulates quantum computation.\\
Project: \url{http://github.com/watkinsr/SQASM}\\
Thesis (PDF): \url{http://github.com/watkinsr/sqasm-thesis}\\

{\bf 2D SDL RPG Engine (C++)} {\bf \hfill 2013}\\
Framework to make 2D RPG's. Over 3000 lines of code in C++.  \\
Source: \url{http://github.com/watkinsr/SDL-RPG}

%% Break for new page
\newpage
\section{\textsc{Community Involvement}}

{\bf Mentor for Android Game Development MOOC}, FutureLearn Ltd {\bf \hfill 2014-2016}\\
Answering various Java and Android related questions from participants

\section{\textsc{Honors}}

{\bf Software Engineering Winner}, University of Reading {\bf \hfill 2014}\\
{\bf Best Team Participation (The EDGE Project)}, Carshalton College {\bf \hfill 2013}

%% Languages
\section{\textsc{Languages}}

\begin{tabular}[t]{@{} p{1.2in} p{3.75in} @{}}

\textbf{English} & Native\\ 
\textbf{German} & Professional\\ 
\textbf{Chinese} & Basic

\end{tabular}

\end{resume}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
